---
title: "Basemaps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basemaps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
library(leaflet)
library(TargomoR)
```

There are a range of map tiles available through Targomo. They can be added directly to a leaflet map through the `addTargomoTiles()` function, which wraps around `leaflet::addTiles()`. Adding these also requires an API key, which is picked up as usual from your `TARGOMO_API_KEY` environment variable (see `setTargomoVariables()` for information).

## Available Basemaps

The full list of available basemap styles is:

```{r map-styles, echo=FALSE}
cat(paste0(targomoMapStyles(), collapse = "\n"))
```

These should be used with `addTargomoTiles()`, as in:

```{r not-run, eval=FALSE}
leaflet() %>% addTargomoTiles(style = "darkblue-nolabels", api_key = ...)
```

## Demonstration

To see each basemap, change the layer visible on the map below:

```{r basemap-demo, echo=FALSE}
l <- leaflet()
for (style in targomoMapStyles()) {
  l <- l %>% addTargomoTiles(style = style, group = style)
}
l %>% addLayersControl(baseGroups = targomoMapStyles(),
                       position = "topright",
                       options = layersControlOptions(collapsed = FALSE)) %>% 
  setView(lat = 51.5, lng = -0.1, zoom = 14)
```

