---
title: "Options"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Options}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The core list of options to pass to the API is summarised in the table below:

| **Option** | **Default Value** | **Explanation** |
| ---------- | ----------------- | --------------- |
| travelType | `"bike"` | The chosen travel type - car, walk, bike or transit (or multiple, for routes) |
| travelTimes | `list(600, 1200, 1800)` | For polygons, the travel times to return (in seconds) |
| intersectionMode | `"union"` | For polygons, the calculation to apply for multiple sources (union or intersection) |
| carRushHour | `FALSE` | Whether to account for rush-hour congestion for the car travelType |
| walkSpeed | `5` | The default walking speed, in km per hour |
| walkUpHillAdjustment | `10` | The percentage increase in walking time if uphill |
| walkDownHillAdjustment | `0` | The percentage increase in walking time if downhill |
| bikeSpeed | `15` | The default bike speed in km per hour |
| bikeUpHillAdjustment | `20` | The percentage increase in cycling time if uphill |
| bikeDownHillAdjustment | `-10` | The percentage in increase in cycling time if downhill |
| transitDate | `NULL` | The date (YYYYMMDD) on which public transport is calculated (NULL defaults to most recent possible) |
| transitTime | `NULL` | The time in seconds from midnight at which public transport is calculated (NULL defaults to now) |
| transitDuration | `NULL` | The time window in which public transport is calculated (s  or `.h.m.s`) |
| transitMaxWalkingTimeFromSource | `NULL` | Max seconds walking from source to bus/train etc |
| transitMaxWalkingTimeToTarget | `NULL` | Max seconds walking from bus/train etc to target |
| transitEarliestArrival | `FALSE` | Whether to calculate public transport routes based on earliest arrival (or shortest duration) |
| transitMaxTransfers | `NULL` | Maximum number of changes on public transport (NULL = no limit) |
| edgeWeight | `"time"` | Whether to calculate based on travel time or distance |
| maxEdgeWeight | `1800` | Maximum time/distance to consider (in seconds/metres or `.h.m.s`) |
| elevation | `FALSE` | Account for terrain elevation? |
| serializer | `"geojson"` | The data serializer to use - geojson or json |
| srid | `4326` | The SRID of the returned data (currently only 4326 supported) |
| minPolygonHoleSize | `NULL` | Minimum area of holes in polygons |
| buffer | `NULL` | Parameters for manipulating the returned polygons |
| simplify | `NULL` | Parameters for manipulating the returned polygons |
| quadrantSegments | `NULL` | Parameters for manipulating the returned polygons |
| decimalPrecision | `NULL` | Parameters for manipulating the returned polygons |

## Debugging

Sometimes, things go wrong! With all the `TargomoR` services, there are several extra arguments which may help you:

### verbose

To each of `getTargomo*` and `addTargomo*`, you can add `verbose = TRUE` - this will print out the full API request to the console so you can check what's going on. Example output is below:

```
-> POST /britishisles/v1/time?key=<TARGOMO_API_KEY> HTTP/1.1
-> Host: api.targomo.com
-> User-Agent: libcurl/7.64.1 r-curl/4.2 httr/1.4.1
-> Accept-Encoding: deflate, gzip
-> Accept: application/json, text/xml, application/xml, */*
-> Content-Length: 448
-> 
>> {
>>   "edgeWeight": "time",
>>   "maxEdgeWeight": 1800,
>>   "elevation": false,
>>   "sources": [
>>     {
>>       "id": 1,
>>       "lat": 51.5007,
>>       "lng": -0.1246,
>>       "tm": {
>>         "bike": {
>>           "speed": 15,
>>           "uphill": 20,
>>           "downhill": -10
>>         }
>>       }
>>     }
>>   ],
>>   "targets": [
>>     {
>>       "id": 1,
>>       "lat": 51.5055,
>>       "lng": -0.0754
>>     },
>>     {
>>       "id": 2,
>>       "lat": 51.5117,
>>       "lng": -0.1246
>>     }
>>   ]
>> }

<- HTTP/1.1 200 
<- Date: Wed, 20 Nov 2019 22:59:11 GMT
<- Content-Type: application/json
<- Content-Length: 109
<- Connection: keep-alive
<- Access-Control-Allow-Origin: *
<- Access-Control-Allow-Headers: origin, content-type, accept, authorization, x-requested-with
<- Access-Control-Allow-Methods: GET, POST, PUT, DELETE, OPTIONS, HEAD
<- Content-Encoding: gzip
<- Server: Targomo | service.targomo.com
<- Strict-Transport-Security: max-age=63072000; includeSubDomains; preload
<- X-Frame-Options: DENY
```

### progress

For long-running requests you can add a progress bar with `progress = TRUE`:

```
|==========================                           | 50%
```

### config

If you need to set extra config settings for using `httr`, do so with the `config` argument. A common use case might be if you're behind a proxy server - in this case you would do (for example):

```{r eval=FALSE}
getTargomoTimes(source_data = sources, target_data = targets,
                config = httr::use_proxy(url = "your.proxy.domain", port = 1234))
```

### timeout

If you've got long requests that need more time and are deploying your code in an environment with a default curl timeout (often 10 seconds), try using `timeout = n`, where n is the number of seconds to wait before giving up. Internally this is passed to `httr::timeout`.

