---
title: "Polygons"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Polygons}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
library(leaflet)
library(TargomoR)

```

Isochrone polygons are a great way of visualising complex travel-time datasets in a powerful way - what does "half an hour away" really look like? With `TargomoR` you can add them straight into a `leaflet` map, or get the data in a convenient form for analysis such as testing intersections with known boundaries (i.e. is any part of this region within half an hour of that point?).

## Getting the Data

For the isochrone polygon service, `getTargomoPolygons()` returns a Simple Feature Collection of 2 fields. The fields are:

* time - the time in seconds of each isochrone
* area - the area in square metres of the isochrone

Each feature is a POLYGON (or MULTIPOLYGON). There is one feature per time specified in the `travelTimes` argument of `targomoOptions()` - see the vignette on [Options](https://cwthom.github.io/TargomoR/articles/Options.html) for more information.

```{r get-polygon}
# set some source data
source <- data.frame(id = "Big Ben", lat = 51.5007, lng = -0.1246)

# query the API
polygons <- getTargomoPolygons(source_data = source,
                               source_lat = ~lat, source_lng = ~lng,
                               options = targomoOptions(travelType = "bike"))

# inspect the output
polygons
```

## Integration with Leaflet

If we want to integrate this into a leaflet map, you can either:

* draw an existing polygons object with `drawTargomoPolygons()`, or;
* combine the API call and drawing with `addTargomoPolygons()`, or;
* write your own drawing function using `leaflet::addPolygons`

The second option looks like:

```{r polygon-example, message=TRUE, warning=TRUE}
# set some source data
source <- data.frame(id = "Big Ben", lat = 51.5007, lng = -0.1246)

# combine the API call and drawing using `addTargomoPolygons`
leaflet() %>% 
  addTargomoTiles() %>% 
  addTargomoPolygons(source_data = source,
                     options = targomoOptions(travelType = "bike"))
```

## Drawing Options

Using `addTargomoPolygons()` you can customise the way the polygons appear on the map with a call to `polygonDrawOptions()`. The options available are:

| **Option**   | **Default**                      | **Meaning**                                        |
| ------------ | -------------------------------- | -------------------------------------------------- |
| stroke       | `TRUE`                           | Should the polygons have a border?                 |
| weight       | `5`                              | The border stroke-weight                           |
| color        | `list("red", "orange", "green")` | The border color                                   |
| opacity      | `0.5`                            | The border opacity                                 |
| fill         | `TRUE`                           | Should the interior of the polygons be filled?     |
| fillColor    | `color`                          | The interior fill color (defaults to border color) |
| fillOpacity  | `0.2`                            | The fill opacity                                   |
| dashArray    | `NULL`                           | The border dash pattern                            |
| smoothFactor | `1`                              | How much to simplify the polylines                 |
| noClip       | `FALSE`                          | Disable polyline clipping?                         |

For example, if we wish to re-create the map above, but with opaque polygons in shades of blue with thin black outlines, we can do the following (this time using `drawTargomoPolygons()`):

```{r polygon-example-2}
leaflet() %>% 
  addTargomoTiles() %>% 
  drawTargomoPolygons(polygons = polygons,
                      drawOptions = polygonDrawOptions(
                       weight = 1, color = "black", opacity = 1,
                       fillColor = c("blue", "dodgerblue", "skyblue"),
                       fillOpacity = 1
                     ))
```
