---
title: "Routes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Routes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
library(leaflet)
library(TargomoR)
```

TODO: Introduction

## Getting the Data

For the routing service, `getTargomoRoutes` returns a named nested list. The names are the travel modes given in the `travelType` option (specifying multiple modes will make multiple calls to the API).

Within each travel mode is a list of the returned routes - one for each source/target combination where a route has been found. Each route is a data.frame, containing the source and target IDs, and a `features` data.frame of a simple feature collection (class 'sf'). This contains: 

* points - the source and target points of the route, as POINT objects.
* walk, bike, car, transit - the routes by each mode of transport (where requested) as LINESTRING objects.
* transfers - points where public transport changes (e.g. change bus) as POINT objects.

Each SFC also contains fields giving the start and end names of the LINESTRINGs, the length of time the section takes and the distance in metres. 

For example, for two routes by bike, the output will look like:

```{r get-route}
# set source and target data
source <- data.frame(id = "Big Ben", lat = 51.5007, lng = -0.1246)
target <- data.frame(id = c("Tower Bridge", "Covent Garden"),
                     lat = c(51.5055, 51.5117),
                     lng = c(-0.0754, -0.1246))

# query the API
routes <- getTargomoRoutes(source_data = source, target_data = target,
                           source_lat = ~lat, source_lng = ~lng,
                           target_lat = ~lat, target_lng = ~lng,
                           source_id = ~id, target_id = ~id,
                           options = targomoOptions(travelType = "bike"))

# examine the structure
str(routes, max.level = 3, give.attr = FALSE)
```

The `features` object for the first route will look like:

```{r get-route-inner}
routes$bike[[1]]$features
```

## Integration with Leaflet

The `TargomoR` package lets you easily visualise your route data. You can either:

* draw an existing routes object with `drawRoutes`, or;
* combine the API call and drawing with `addTargomoRoutes`, or;
* write your own drawing function using `leaflet::addPolylines`

In this example, we use `addTargomoRoutes` to show the cycling routes above.

```{r route-example}
leaflet() %>% 
  addTargomoTiles() %>% 
  addTargomoRoutes(source_data = source, source_id = ~id,
                   target_data = target, target_id = ~id,
                   options = targomoOptions(travelType = "bike"))
```

## Drawing Options

Using `addTargomoRoutes` or `drawRoutes` you can customise the way the routes appear on the map with a call to `routeDrawOptions`. The options available are:

| **Option**        | **Default**                      | **Meaning**                                                |
| ----------------- | -------------------------------- | ---------------------------------------------------------- |
| showMarkers       | `TRUE`                           | Should the source/target points be marked?                 |
| showTransfers     | `TRUE`                           | Should the public transport changes be marked?             |
| {travel}Color     | car = `"blue"`, bike = `"orange"`, walk = `"green"`, transit = `"red"` | The route line color |
| {travel}Weight    | `5` for all travel types         | The route line width                                       |
| {travel}DashArray | walk = `"1,10"`, other = `NULL`  | The route dash pattern                                     |
| transferColor     | `"blue"`                         | The color for transfer circle markers                      |
| transferRadius    | `10`                             | The radius for transfer circle markers                     |

Changing these, we could for instance make the map above but with purple dotted lines (and here we'll use `drawRoutes`):

```{r route-example-2}
leaflet() %>% 
  addTargomoTiles() %>% 
  drawRoutes(routes = routes, 
             drawOptions = routeDrawOptions(
               bikeColour = "purple",
               bikeDashArray = "10,15"
             ))
```
