---
title: "Introduction to TargomoR"
author: "Chris Mason-Thom"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to TargomoR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
library(TargomoR)
```

The `TargomoR` package is designed to be an R interface to the [Targomo](https://www.targomo.com/) travel time service, through their [REST API](https://docs.targomo.com/core/). The goal is to make it easy for R users to access the data, so they can spend more time doing analysis and less time wrestling with API documentation.

The functions in `TargomoR` are designed to integrate with those of `leaflet` - functions for adding features and tiles to a `leaflet` map for example all take the form `addTargomo*`, and can be piped together using `%>%`. 

Underlying the functions to talk to the API is the `httr::POST` function. Each request is composed by translating your data and options into a suitable JSON request, `POST`ing it to the API, and processing the JSON response into an `sf` object.

## Services Available

Targomo provides a range of travel-time services as end-points from their API. Currently supported services are detailed in the table below. Please see the linked articles for more information on each service.

| **Service**                                                          | **Key Functions**                              | 
| -------------------------------------------------------------------- | ---------------------------------------------- |
| [Basemaps](https://cwthom.github.io/TargomoR/articles/Basemaps.html) | `addTargomoTiles()`, `targomoMapStyles()`      |
| [Polygons](https://cwthom.github.io/TargomoR/articles/Polygons.html) | `getTargomoPolygons()`, `addTargomoPolygons()`, `polygonDrawOptions()` |
| [Routes](https://cwthom.github.io/TargomoR/articles/Routes.html)     | `getTargomoRoutes()`, `addTargomoRoutes()`, `routeDrawOptions()`     |
| [Times](https://cwthom.github.io/TargomoR/articles/Times.html)       | `getTargomoTimes()`, `addTargomoTimes()`, `timeDrawOptions()`       |
| [Options for All Services](https://cwthom.github.io/TargomoR/articles/Options.html) | `targomoOptions()`              |

As well as the `addTargomo*` functions there are also corresponding `getTargomo*` functions which return the data from the API as a usable R object. This is particularly useful if you're conducting further analysis with the data, rather than immediately visualising it.

## Example

The following code snippet shows how easy it is to add detailed routing data to a `leaflet` map, in just a few function calls. Try clicking the red public transport lines for more information about the route!

```{r example}
# load packages
library(leaflet)
library(TargomoR)

# set source and target data
source <- data.frame(id = "Big Ben", lat = 51.5007, lng = -0.1246)
target <- data.frame(id = "Tower Bridge", lat = 51.5055, lng = -0.0754)

# create map and add a basemap and routes
leaflet() %>% 
  addTargomoTiles(style = "basic") %>% 
  addTargomoRoutes(source_data = source,
                   target_data = target,
                   options = targomoOptions(
                     travelType = "transit",
                     transitMaxTransfers = 1
                   )) %>% 
  addTargomoAttribution(position = "bottomleft")
```

Check out the detailed [articles](https://cwthom.github.io/TargomoR/articles) for more information.
