---
title: "Times"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Times}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
library(leaflet)
library(TargomoR)
```

TODO: Introduction

## Getting the Data

For the time service, `getTargomoTimes` returns a Simple Feature Collection of 4 fields. Each feature is a POINT (corresponding to the target point), and the fields are:

* sourceId, targetId - given IDs for the points, or inferred numeric IDs if none supplied
* travelType - the travel mode (can supply multiple as with routes)
* travelTime - the time taken in seconds to get from the source to the target

```{r get-times, echo=FALSE}
# set source and target data (TODO: Add multiple (random) targets)
source <- data.frame(id = "Big Ben", lat = 51.5007, lng = -0.1246)
target <- data.frame(id = "Tower Bridge", 
                     lat = 51.5055,
                     lng = -0.0754)

# query the API
times <- getTargomoTimes(source_data = source, target_data = target,
                         source_lat = ~lat, source_lng = ~lng,
                         target_lat = ~lat, target_lng = ~lng,
                         source_id = ~id, target_id = ~id,
                         options = targomoOptions(travelType = "car"))

# examine the output
times
```

## Integration with Leaflet

TODO: Add leaflet example
