---
title: "Times"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Times}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
library(leaflet)
library(TargomoR)
```

One of the most powerful features of Targomo is the ability to quickly get A-to-B travel times for a multitude of source/target combinations. These make for great 'heatmap' visuals, or can be used for further analysis and aggregation.

## Getting the Data

For the time service, `getTargomoTimes()` returns a Simple Feature Collection of 4 fields. Each feature is a POINT (corresponding to the target point), and the fields are:

* `sourceId`, `targetId` - given IDs for the points, or inferred numeric IDs if none supplied
* `travelType` - the travel mode (can supply multiple as with routes)
* `travelTime` - the time taken in seconds to get from the source to the target

```{r get-times, echo=TRUE}
# load package
library(TargomoR)

# set source and target data
source <- data.frame(id = "Big Ben", lat = 51.5007, lng = -0.1246)
target <- data.frame(id = c("Tower Bridge", "Covent Garden"),
                     lat = c(51.5055, 51.5117),
                     lng = c(-0.0754, -0.1246))

# query the API
times <- getTargomoTimes(source_data = source, target_data = target,
                         source_lat = ~lat, source_lng = ~lng,
                         target_lat = ~lat, target_lng = ~lng,
                         source_id = ~id, target_id = ~id,
                         options = targomoOptions(travelType = "car"))

# examine the output
times
```

## Integration with Leaflet

As with the polygon and route services, there are three ways to add time data to a map:

* use `drawTargomoTimes()` to send your times dataset to the map
* use `addTargomoTimes()` to combine the API call and drawing in one
* write your own drawing function using `leaflet::addMarkers` or `leaflet::addCircleMarkers`

In the example below, we'll generate some random points and use `addTargomoTimes()` to combine requesting the data and adding it to the map:

```{r time-example}

# get random target data (source data = Big Ben as before)
targets <- data.frame(id = 1:100,
                      lat = runif(100, min = 51.45, max = 51.55),
                      lng = runif(100, min = -0.17, max = -0.07))

leaflet() %>% 
  addTargomoTiles() %>% 
  addTargomoTimes(source_data = source, source_id = ~id,
                  target_data = targets, target_id = ~id,
                  options = targomoOptions(travelType = "bike"))
```

## Drawing Options

Using `addTargomoTimes()` or `drawTargomoTimes()` you can customise the way the routes appear on the map with a call to `timeDrawOptions()` and `timeLegendOptions()`. The options available are:

**timeDrawOptions**

| **Option**        | **Default**                      | **Meaning**                                                |
| ----------------- | -------------------------------- | ---------------------------------------------------------- |
| palette           | `"viridis"`                      | A colour palette name e.g. "Blues", "viridis"              |
| type              | `"numeric"`                      | "numeric" or "bin" - continuous or discrete groupings      |
| maxTime           | `1800`                           | Maximum time to allow for (in seconds)                     |
| reverse           | `FALSE`                          | Reverse the colour palette?                                |
| bins              | `c(600, 1800)`                   | A number of bins or vector of cut points (only for "bin" type) |
| legend            | `TRUE`                           | Add a legend to the map                                    |
| legendOptions     | `timeLegendOptions()`            | A list of legend options - see below                       |
| radius            | `10`                             | Radius of the circle markers used                          |
| stroke            | `TRUE`                           | Whether to draw the marker border                          |
| weight            | `3`                              | Stroke weight in pixels                                    |
| color             | `"black"`                        | Stroke colour                                              |
| opacity           | `0.5`                            | Stroke opacity                                             |
| fill              | `TRUE`                           | Fill the markers with colour (from palette)?               |
| fillOpacity       | `0.5`                            | Fill opacity                                               |

**timeLegendOptions**

| **Option**        | **Default**                      | **Meaning**                 |
| ----------------- | -------------------------------- | --------------------------- |
| position          | `"topright"`                     | Legend position on map      |
| title             | `"Travel Times"`                 | Legend title                |
| layerId           | `NULL`                           | Leaflet layer id for legend |

Changing some of these options, we could re-draw the above map with smaller markers, using the `inferno` palette and white borders, with a different legend title and discrete bins:

```{r time-example-2}
leaflet() %>% 
  addTargomoTiles() %>% 
  addTargomoTimes(source_data = source, target_data = targets,
                  options = targomoOptions(travelType = "bike"),
                  drawOptions = timeDrawOptions(
                    palette = "inferno",
                    type = "bin", bins = c(0, 300, 600, 900, 1200, 1800),
                    color = "white", radius = 5,
                    opacity = 1, fillOpacity = 1,
                    legendOptions = timeLegendOptions(
                      position = "bottomleft",
                      title = "Cycling Times"
                    )
                  )
  )
```
                
                  



